Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-06-20 presentation/presentation.tex
[major] ppt for air2017

\section{Results}
\begin{frame}{Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

@@

>>>>

\section{Experiments and results}
\begin{frame}{Experiments and results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

@@

\begin{frame}{Accuracy measurement}
	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
	\begin{columns}[t]
		\begin{column}{0.4\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{inclination_plus}
				%\caption{Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{success_rate}
				%\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Failure detection using end-effector forces}
	\begin{exampleblock}{Procedure}
		\begin{enumerate}
			\item Each trajectory is computed by calculating the mean. 
			\item The force value is norm of force applied in all three Cartesian directions.
		\end{enumerate}
	\end{exampleblock}

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.3\textwidth}
			\begin{figure}
				\includegraphics[width=0.8\textwidth]{failure_scenario_2}
				\caption{A failure scenario}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=0.9\textwidth]{position_force}
				\caption{Forces acting on left arm of Baxter}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}
